% arara: pdflatex: { synctex: yes }
% arara: makeindex: { style: ctuthesis }
% arara: bibtex

% The class takes all the key=value arguments that \ctusetup does,
% and a couple more: draft and oneside
\documentclass[twoside]{ctuthesis}


\ctusetup{
	%preprint = \ctuverlog,
	mainlanguage = english,
	otherlanguages = {czech},
	title-czech = {Taktilní průzkum terénu robotickou rukou},
	title-english = {Haptic terrain exploration with robotic arm},
	subtitle-czech = {},
	subtitle-english = {},
	doctype = M,
	faculty = F3,
	department-czech = {Katedra kybernetiky},
	department-english = {Department of Cybernetics},
	author = {Martin Burian},	supervisor = {doc. Tomáš Svoboda, Ph.D.},
	supervisor-address = {},
	supervisor-specialist = {},
	fieldofstudy-english = {Open informatics},
	subfieldofstudy-english = {Computer vision and digital image},
	fieldofstudy-czech = {Otevřená informatika},
	subfieldofstudy-czech = {Počítačové vidění a digitální obraz},
	keywords-czech = {mapování, robotická ruka, plánování pokrývajících cest, taktilní vnímání},
	keywords-english = {mapping, robotic arm, coverage path planning, tactile sensing},
	day = 9,
	month = 1,
	year = 2017,
	specification-file = {zadani.pdf},
	front-specification = true,
%	front-list-of-figures = false,
	front-list-of-tables = false,
%	monochrome = true,
%	layout-short = true,ded. One way to do is with a \makebox command (6). This is the LaTeX code produce made by the above 
}

\ctuprocess

\addto\ctucaptionsczech{%
	\def\supervisorname{Vedoucí}%
	\def\subfieldofstudyname{Studijní program}%
}

\ctutemplateset{maketitle twocolumn default}{
	\begin{twocolumnfrontmatterpage}
		\ctutemplate{twocolumn.thanks}
		\ctutemplate{twocolumn.declaration}
		\ctutemplate{twocolumn.abstract.in.titlelanguage}
		\ctutemplate{twocolumn.abstract.in.secondlanguage}
		\ctutemplate{twocolumn.tableofcontents}
		\ctutemplate{twocolumn.listoffigures}
	\end{twocolumnfrontmatterpage}
}

% Theorem declarations, this is the reasonable default, anybody can do what they wish.
% If you prefer theorems in italics rather than slanted, use \theoremstyle{plainit}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{note}
\newtheorem*{remark*}{Remark}
\newtheorem{remark}[theorem]{Remark}

\setlength{\parskip}{5ex plus 0.2ex minus 0.2ex}



% Abstract in Czech
\begin{abstract-czech}
Při záchranných misích mohou senzory robotu Absolem používaného v projektu TRADR selhat díky nepříznivým podmínkám prostředí, jako například kouř nebo prach. Bez senzorických dat je další pohyb robotu obtížný a nebezpečný. Robotická ruka, kterou je robot vybaven, může být v takovýchto situacích použita pro získání informací o prostředí snímáním taktilních měření. Navrhli jsme algoritmus, který při exploraci ruku navádí, spolu s metodami pro řízení ruky a snímání měření z bezpečné vzdálenosti. Systém jsme implementovali a otestovali jak v simulovaném, tak v reálném prostředí.
\end{abstract-czech}



% Abstract in English
\begin{abstract-english}
In search and rescue missions, the sensors on the Absolem mobile robot used in the TRADR project can fail due to environmental conditions like smoke and dust, making further robot operation difficult and dangerous for the robot. In such cases, the robot-mounted robotic arm can be used to gain information about the environment by obtaining tactile measurements from it. We propose an algorithm to guide the arm during the exploration, along with methods to control the arm movement and to gather the measurements with a 3D force sensor from safe distance. The system is implemented and put to the test in both simulated experiments and real world trials.
\end{abstract-english}



% Acknowledgements / Podekovani
\begin{thanks}
I would like to thank my supervisor Tomáš Svoboda for his infinite patience, and to my partner Zuzana who helped me survive the creation of this thesis.
\end{thanks}



% Declaration / Prohlaseni
\begin{declaration}
I declare that the presented work was developed independently and that I have listed all sources of information used within in accordance with the methodical instructions for observing principles in preparation of university theses.

Prague, \ctufield{day}.~\monthinlanguage{title}~\ctufield{year}

\makebox[10em]{\dotfill}
\end{declaration}

% Only for testing purposes
%\usepackage[pagewise]{lineno}

%\usepackage{graphicx}
\graphicspath{{./}{./figures/}}
\usepackage{subfiles}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup[subfigure]{labelformat=simple,labelsep=period}
\usepackage{algorithm}
\usepackage{algpseudocode}

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%

\providecommand*{\diff}{\textrm{d}\,}
\providecommand*{\pdiff}{\partial\,}
\newcommand*{\m}[1]{\(#1\)}
\newcommand*{\unit}[1]{\; \textrm{[#1]}}
\newcommand*{\degr}{^\circ}
\newcommand*{\uvz}[1]{``#1''}
\newcommand*{\quot}[2]{\textit{\uvz{#1}}\cite{#2}}
\renewcommand*{\vec}[1]{\mathbf{#1}}
\newcommand*{\mat}[1]{\mathbf{#1}}
\newcommand*{\half}{^1\!/_{\!2}}
\newcommand*{\difrac}[2]{^{#1\!}/_{\!#2}}
\newcommand*{\R}{I\!\!R}
\newcommand*\colvec[3][]{
    \begin{pmatrix}\ifx\relax#1\relax\else#1\\\fi#2\\#3\end{pmatrix}
}
\newcommand*{\dvec}[1]{\dot{\vec{#1}}}

\definecolor{code-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{code-gray}{\texttt{\detokenize{#1}}}}



\newcounter{todo}
\newcommand{\TODO}[1]{\refstepcounter{todo}%
{\color{red}TODO:~#1}%
\addcontentsline{tod}{section}{\thetodo~#1}}%

\newcommand{\REV}[1]{\refstepcounter{todo}%
{\color{orange}#1??}%
\addcontentsline{tod}{section}{\thetodo~#1}}%

\makeatletter
%\newcommand\todoname{TODO}
\newcommand\listtodoname{List of todos!}
\newcommand\listoftodos{%
  \section*{\listtodoname}\@starttoc{tod}}
\makeatother


\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\setlength{\parskip}{2ex plus 0.2ex minus 0.1ex}
\setcounter{tocdepth}{1}

\algdef{SE}[DOWHILE]{Do}{doWhile}{\algorithmicdo}[1]{\algorithmicwhile\ #1}%

%%%% BODY %%%%
\begin{document}

\maketitle

%\listoftodos


\subfile{ch_intro}


\subfile{ch_robot}


\subfile{ch_exploration}


\subfile{ch_cpp}


\subfile{ch_implementation}


\subfile{ch_experiments}


\subfile{ch_conclusion}

\appendix

\bibliographystyle{unsrt}
\bibliography{buriama8_dp}

\chapter{CD contents}

The CD contains all the source codes we created in directory \code{src}.

A digital copy of this thesis is in the root of the CD as \code{buriama8_dp.pdf}



\end{document}


%\ctutemplate{specification.as.chapter}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
